Active Learning from Blackbox to Timed Connectors

### 2016-04-14 shortpaper/paper.tex
.

Similarly, we can use PMMs to describe the behavior of other basic timed Reo
channels. Now we show how to compose these channels into more complicated connectors.

\liyi{Actually I'm not sure if omitting definition of prod and link is a good idea. Generally I
think this paper should focus on two parts: definition of PMM and optimization of L* algorithm.}

@@

\section{From Blackbox to Timed Connectors} 
\label{sec:activelearning}
In this section, we use L* algorithm to extract Reo coordinators from blackbox
implementations in 3 steps:
\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. 
The input and output symbols of the blackbox implementation are provided as $\mathcal{I}$ and
$\mathcal{O}$, and the blackbox implementation is supposed to be equivalent to a Mealy machine where
all states are reachable.

\subsection{Active Learning: Overview}
In this section, we briefly introduce the main ideas of active automata learning.

Active learning \cite{settles2010active} is a special case of semi-supervised machine learning where
a learning algorithm is able to interactively query the target systems to obtain the desired outputs
under certain inputs. By well-designed query strategy, active learning is able to obtain more
accurate models with smaller data-set.

\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=.5\textwidth]{./images/activelearning.png}
  \end{center}
  \caption{Active Automata Learning}
  \label{fig:activelearning}
\end{figure}

@@

Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
all communication with the model. The oracle also serves as a so-called \emph{Minimal Adequate Teacher}
interface, which is responsible for two types of queries.

@@

More details on the active automata learning algorithm will be presented in Section
\ref{sec:activelearning}.

@@

%The whole L* algorithm can be concluded as follows.
%\begin{algorithm} 
  %\caption{L*} 
  %\label{alg:lstar}
  %\KwIn{Oracle interfaces $mq,eq$, Input actions $\mathcal{I}$}
  %\KwOut{Observation table $obs$} 
  %$obs.S$ initialized as empty\;
  %$obs.D$ initialized as $\{[i]|i\in\mathcal{I}\}$\;
  %\Repeat{$ce=true$}{
    %$obs$ = EncloseTable($mq$, $\mathcal{I}$, $obs$)\;
    %$ce=eq(obs)$\;
    %\If {$ce\neq true$} {
      %$obs.D$.append(Suffix$(ce, obs)$)\;
    %}
  %}
  %\Return $obs$\; 
%\end{algorithm}

@@

With cache applied, we have made considerable reduction on the calls of membership queries. The results
can be found in Table \ref{tabel:cacheoptimization}.

\section{Conclusion and Future Work}
In this paper, we come up with an approach to extract timed connectors from blackbox
implementations. We propose \emph{parameterized Mealy machine} to describe the behavior of Reo
connectors. Then we define the product operator and link operator, which can be used to
construct complex connectors from simpler ones.
Besides, we show how PMMs behave as the bridge between Reo connectors and concrete Mealy
machines with timed action T provided.

>>>>

Similarly, we can use PMMs to describe the behavior of other basic timed Reo
channels. In Reo, as mentioned before, we compose complex connectors with simpler ones and basic
channels recursively. Operator \emph{prod} and \emph{link} are used to apply such composing
operation.

\begin{definition}[prod]
  For two PMMs $\mathcal{PM}_1$ and $\mathcal{PM}_2$, we use the \emph{prod} operator
  $\mathcal{PM'} = prod(\mathcal{PM}_1,\mathcal{PM}_2)$ to denote their production, where every
  sink-end in $\mathcal{PM}_1$ is connected with it's homonymic source-end in $\mathcal{PM}_2$.
\end{definition}

\begin{definition}[link]
  For a PMM $\mathcal{PM}$, we use the \emph{link} operator to connect its sink-end $\OUT$ with its
  source-end $\IN$, formally denoted as $\mathcal{PM}' = link(\mathcal{PM}, \OUT, \IN)$.
\end{definition}

@@

\section{From Blackbox to Timed Connectors} 
\label{sec:activelearning}
In this section, we provide a brief introduction on the well-known L* algorithm, which is used
to extract Reo coordinators from blackbox implementations in 3 steps:
\emph{constructing hypothesis}, \emph{enclosing hypothesis} and \emph{validating hypothesis}. 
The input and output symbols of the blackbox implementation are provided as $\mathcal{I}$ and
$\mathcal{O}$, and the blackbox implementation is supposed to be equivalent to a Mealy machine where
all states are reachable.

\subsection{An Overview of Active Learning}
Active learning \cite{settles2010active} is a special case of semi-supervised machine learning where
a learning algorithm is able to interactively query the target systems to obtain the desired outputs
under certain inputs. By well-designed query strategy, active learning is able to obtain more
accurate models with smaller data-set.

\begin{figure}[ht]
  \begin{center}
    \includegraphics[width=.45\textwidth]{./images/actl.pdf}
  \end{center}
  \caption{Active Automata Learning}
  \label{fig:activelearning}
\end{figure}

@@

Such a model is encapsulated as a \emph{teacher} by the \emph{Oracle}, which handles
all communication with the model. The oracle also serves as a so-called \emph{Minimal Adequate
Teacher} \cite{DBLP:journals/iandc/Angluin87}
interface, which is responsible for two types of queries.

@@

@@

\subsection{L* Algorithm}
The whole L* algorithm can be concluded as follows.
\begin{algorithm} 
  \caption{L*} 
  \label{alg:lstar}
  \KwIn{Oracle interfaces $mq,eq$, Input actions $\mathcal{I}$}
  \KwOut{Observation table $obs$} 
  $obs.S$ initialized as empty\;
  $obs.D$ initialized as $\{[i]|i\in\mathcal{I}\}$\;
  \Repeat{$ce=true$}{
    $obs$ = EncloseTable($mq$, $\mathcal{I}$, $obs$)\;
    $ce=eq(obs)$\;
    \If {$ce\neq true$} {
      $obs.D$.append(Suffix$(ce, obs)$)\;
    }
  }
  \Return $obs$\; 
\end{algorithm}

In this algorithm, when we use \emph{observation tables} to represent hypothetical models.

@@

With the help of cache technique, we have made considerable reduction on the calls of membership queries. The results
can be found in Table \ref{tabel:cacheoptimization}.

\section{Conclusion and Fu ture Work}
In this paper, we come up with an approach to extract timed connectors from blackbox
implementations. We propose \emph{parameterized Mealy machine} to describe the behavior of Reo
connectors. Then we define the product operator and link operator, which can be used to
construct complex connectors from simpler ones.
Besides, we show how PMMs behave as the bridge between Reo connectors and concrete Mealy
machines with timed action T provided.
